The pollination trade-off

### 2018-11-06 paper/manuscript.Rmd
Update changelog

* Use AICc instead of AIC (no change in results)
* To keep signature of phenology, absolute flower counts (log-transformed) are used instead of relative abundances
* Columns in the trait matrix for phenology are scaled so that it doesn't count 5 times as much as other traits
* Boostraping resampling worked

>>>>

* Use AICc instead of AIC (no change in results)
* To keep signature of phenology, absolute flower counts (log-transformed) are used instead of relative abundances
* Columns in the trait matrix for phenology are scaled so that it doesn't count 5 times as much as other traits
* Only modeling open and bagged pollen counts, using the bagged as a control. So not showing the results of the relative pollen count (open vs bagged flowers) anymore
* Introduced visit efficiency instead of share in the pollen pool as it is a better predictor. 
* Use a PCA of the explanatory variables to understand different plant strategies
